Precise predictions for same-sign W-bosons scattering at the LHC

### 2018-02-16 Draft/definition.tex
Updated definitions section

The scattering of two positively charged $\PW$ bosons with their subsequent leptonic decay proceeds at the LHC through the partonic process:
%
\begin{equation}
\Pp\Pp\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}\,\Pj\Pj+\mathrm{X}.
\end{equation}

This process possesses three LO contributions of different orders.
The first one is of order $\mathcal{O}{\left(\alpha^{6}\right)}$ and is referred to as EW contribution.
In addition to typical VBS contributions, as shown on the left of Fig.~\ref{diag:LO}, it also features $s$-channel contributions.
Note that we define $s$-, $t$-, and $u$-channel contributions by looking at the process which is contained by only looking at the quark lines, {\emph i.e.} $s$-channel denotes all Feynman diagrams where the two initial-state partons are connected by a continuous fermion line, and $u$-channel is the contribution with crossed fermion lines, which appears for identical quarks or anti-quarks in the final state.
The $s$-channels will play a particular role in the study of the various contributions in Sec.~\ref{subsec:contributions}.
Some of them take the form of decay chains, for example the diagram represented in the middle of Fig.~\ref{diag:LO}, while others are tri-boson contributions (right of Fig.~\ref{diag:LO}).
When using approximations, care must be taken that only gauge-invariant subsets are considered to obtain physically meaningful results. We will discuss the commonly-used possible choices in detail in the next section.

@@

In experimental measurements, special VBS-cuts are designed to enhance the EW contribution over the QCD one.
These cuts are based on the fact that the two contributions have different kinematical behaviour.
The EW contribution is characterised by two jets with large rapidities as well as a large invariant mass.
The two $\PW$ bosons are mostly produced centrally.
This is in contrast with the QCD contribution which favours jets in the central region.
Therefore, the event selection usually involves rapidity-difference and invariant-mass cuts for the jets.
This will be further discussed in Sec.~\ref{subsec:contributions}.

\begin{figure*}[t]
\begin{center}
          \includegraphics[width=0.30\linewidth]{feynman/LO_EW_5}
          \raisebox{.5ex}{\includegraphics[width=0.35\linewidth]{feynman/LO_EW_2}}
          \raisebox{-1.8ex}{\includegraphics[width=0.32\linewidth]{feynman/LO_EW_3}}
\end{center}
        \caption{Sample tree-level diagrams that contribute to the process $\Pp\Pp\to\mu^+\nu_\mu\Pe^+\nu_{\Pe}\Pj\Pj$ at order $\mathcal{O}{\left(\alpha^{6}\right)}$.
        In addition to typical VBS contribution (left), this order also possesses $s$-channel (middle) and tri-boson contributions (right). }
\label{diag:LO}
\end{figure*}

>>>>

The scattering of two positively charged $\PW$ bosons with their subsequent leptonic decay proceeds at the LHC through the partonic process\AK{This is only one such process...}:
%
\begin{equation}
\Pp\Pp\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}\,\Pj\Pj+\mathrm{X}.
\end{equation}

This process possesses three LO contributions of different orders.
The first one is of order $\mathcal{O}{\left(\alpha^{6}\right)}$ and is referred to as the EW contribution.
In addition to typical VBS contributions, as shown on the left of Fig.~\ref{diag:LO}, it also features $s$-channel contributions.
Note that we define $s$-, $t$-, and $u$-channel contributions by looking at the process which is contained by only looking at the quark lines, {\emph i.e.} $s$-channel denotes all Feynman diagrams where the two initial-state partons are connected by a continuous fermion line, and $u$-channel is the contribution with crossed fermion lines, which appears for identical quarks or anti-quarks in the final state.\AK{This sentence makes no sense to me. How about: ``Note that we define $s$-, $t$-, and $u$-channel contributions by looking at the quark lines. $s$-channel denotes all the diagrams where the final state quarks are produced from the decay of a vector boson.'' Or am I missing something?}
The $s$-channels will play a particular role in the study of the various contributions in Sec.~\ref{subsec:contributions}.
Some of them take the form of decay chains, for example the diagram represented in the middle of Fig.~\ref{diag:LO}, while others are tri-boson contributions (right of Fig.~\ref{diag:LO}).
When using approximations, care must be taken that only gauge-invariant subsets are considered to obtain physically meaningful results. We will discuss the commonly-used possible choices in detail in the next section.

@@

In experimental measurements, special VBS-cuts are designed to enhance the EW contribution over the QCD one.
These cuts are based on the fact that the two contributions have different kinematical behaviour.
The EW contribution is characterised by two jets with large rapidities as well as a large invariant mass.
The two $\PW$ bosons are mostly produced centrally.
This is in contrast to the QCD contribution which favours jets in the central region.
Therefore, the event selection usually involves rapidity-difference and invariant-mass cuts for the jets.
This will be further discussed in Sec.~\ref{subsec:contributions}.
\AK{Should we also discuss the definition of the process at NLO - ie point out that at this level one can no longer distinguish EW/QCD production?}
\begin{figure*}[t]
\begin{center}
          \includegraphics[width=0.30\linewidth]{feynman/LO_EW_5}
          \raisebox{.5ex}{\includegraphics[width=0.35\linewidth]{feynman/LO_EW_2}}
          \raisebox{-1.8ex}{\includegraphics[width=0.32\linewidth]{feynman/LO_EW_3}}
\end{center}
        \caption{Sample tree-level diagrams that contribute to the process $\Pp\Pp\to\mu^+\nu_\mu\Pe^+\nu_{\Pe}\Pj\Pj$ at order $\mathcal{O}{\left(\alpha^{6}\right)}$.
        In addition to typical VBS contribution (left), this order also possesses $s$-channel (middle) and tri-boson contributions (right). \AK{The text here is in conflict with the main text. Reading this it looks as if s-channel and tri-boson production are two different classifications, but in the main text we say both decay chains and tri-boson production belongs to s-channel.}}
\label{diag:LO}
\end{figure*}
